Supplement History of Cheminformatics as part of Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-09 supplement_history.tex
fixed some typos in refs. minor changes to the text

Bonchev/Rouvrey \cite{bonchevrouvrey1991,bonchevrouvrey2003} and 1992
by Trinastic \cite{Trinajstic1992}.  More recently, Faulon \& Bender
\cite{faulon2010} have edited a collection focusing on algorithms in
cheminformatics, including various applications of graph theory.
Other books focus more on specific topcs such as mathematical

>>>>

Bonchev and Rouvrey \cite{bonchevrouvrey1991,bonchevrouvrey2003} and
1992 by Trinastic \cite{Trinajstic1992}.  More recently, Faulon \&
Bender \cite{faulon2010} have edited a collection focusing on
algorithms in cheminformatics, including various applications of graph
theory.  Other books focus more on specific topcs such as mathematical
